### 2019-02-26 sections/relatedwork.tex
examples of stuff that we didn't include in TopHat

\paragraph{iTasks}
\fixme{Rinus: Waarom geen korte opsomming van iTask features die niet zijn meegenomen in TopHat?}
As mentioned earlier, iTasks is an implementation of \TOP.
iTasks has many features, and its basic combinators are versatile and powerful.
Simpler combinators are implemented by restricting the powerful ones.
This is useful for everyday programming, where having lots of functionality at one's fingertips is convenient and efficient.

@@

\fixme{Rinus: Volgens mij is er wel degelijk een formele semantiek, omdat heel iTask wordt uitgelegd in termen van standaard Clean functies,
en Clean heeft een semantiek (graaf herschrijf systeem).
Dat de beschrijving onhandig (wellicht te low level is) is voor het formeel redeneren over iTask programma's is een beter argument.}
\fixme{Alejandro: What is missing from \TOPHAT to describe i or m Tasks}

>>>>

\paragraph{iTasks}
As mentioned earlier, iTasks is an implementation of \TOP.
iTasks has many features, and its basic combinators are versatile and powerful.
Simpler combinators are implemented by restricting the powerful ones.
This is useful for everyday programming, where having lots of functionality at one's fingertips is convenient and efficient.
\TOPHAT on the other hand does not include the many different variations of the step- and parallel combinators of \ITASKS.
To name two examples, the combinators \verb+(>>|)+ and \verb+(||-)+ are variations of step and parallel that ignore the value of the left task.

@@

\fixme{Rinus: Volgens mij is er wel degelijk een formele semantiek, omdat heel iTask wordt uitgelegd in termen van standaard Clean functies,
en Clean heeft een semantiek (graaf herschrijf systeem).
Dat de beschrijving onhandig (wellicht te low level is) is voor het formeel redeneren over iTask programma's is een beter argument.}
